---
title: "README"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
library(ggplot2)
library(dplyr)
library(fivethirtyeight)
# For reading CSV spreadsheet files:
library(readr)
avg_congress_age <- congress_age %>% 
  group_by(termstart,party) %>% 
  summarise(mean_age=mean(age,na.rm = TRUE)) %>% 
  filter(party == "D"| party == "R")
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
ggplot(data=avg_congress_age, mapping=aes(x=termstart, y=mean_age,color=party))+
  geom_line()+
  coord_cartesian(ylim=c(40,60))+
  labs(
    x="Date",
    y="Average age",
    title="Average Age of Members of Congress",
    subtitle="At start of term, 1947-2013"
  )+
  scale_color_manual(values=c("blue","red"))
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
